Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-12 rapport.tex
minor changes GGM

		\subsubsection{GGM tree}

@@

		\begin{corollary}[Corollary 3 in \cite{FSS11}]\label{complex_bi}
			The arithmetic complexity of computing a Gröbner basis of a generic bilinear system $f_1,...,f_{n_x + n_y}$ with the F5 algorithm is bounded by
			$$\mathcal{O}\left(\binom{n_x + n_y + min(n_x + 1, n_y + 1)}{min(n_x + 1, n_y + 1)}^\omega\right).$$
		\end{corollary}

@@

		\subsubsection{Space complexity of other attacks}

>>>>

		\subsubsection{GGM tree}
		Since most of the values used in the MPC protocol are randomly generated, a technique known as the GGM tree can be employed to transmit only a seed, rather than all the individual random values.

		A GGM tree is essentially a binary tree rooted at a seed, on which a pseudorandom function (PRF) is applied. The PRF must produce an output of twice the bit-length of its input. The first half of the output serves as the root of the left subtree, and the second half as the root of the right subtree. This process is applied recursively until enough leaves are generated, which correspond to the required random values.

		In our case, we do not transmit the seed due to the use of linear secret sharing. Since we typically employ an $(N-1)$-private MPC protocol, we only share the co-path of the $i$-th leaf, which remains hidden from $\mathcal{V}$. As a result, instead of sharing $N$ values, we only need to share $log_2(N)$ values.

		\subsubsection{HyperCube technique}

@@

		\begin{corollary}[Corollary 3 in \cite{FSS11}]\label{complex_bi}
			The arithmetic complexity of computing a Gröbner basis of a generic affine bilinear system $f_1,...,f_{n_x + n_y}$ with the F5 algorithm is bounded by
			$$\mathcal{O}\left(\binom{n_x + n_y + min(n_x + 1, n_y + 1)}{min(n_x + 1, n_y + 1)}^\omega\right).$$
		\end{corollary}

		\begin{corollary}

		\end{corollary}

@@

	\subsection{Attacks summary}
		\begin{table}[h!]
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				Algorithm & Parameters & Time & Memory \\
				\hline
				Exhaustive search & / & 260 & 24 \\
				\hline
				Dinur First & / & 229 & 200 \\
				\hline
				Dinur Second & / & 221 & 172 \\
				\hline
				Crossbred & D=12, d=10, k=130 & 159 & 90 \\
				\hline
				Naive & / & 150 & 15 \\
				\hline
			\end{tabular}
			\caption{Time and memory complexity of given algorithms in powers of 2.
				For Exhaustive search, Dinur First and Dinur second, the estimations were obtained using CryptographicEstimator \cite{EVZ+24}}
		\end{center}
		\end{table}
